---
title: "Picture Predictor Analytics"
author: "Theo Van Rooy"
date: "1/29/2015"
output: html_document
runtime: shiny
---

This document gives some basic stats, plots and information about the data collected by the Picture Prediction app.

Also, some interactive modeling

## Basic Stats

```{r echo=FALSE}
library(rredis)
library(dplyr)
library(ggplot2)
library(RJSONIO)
library(knitr)
library(shiny)
library(lubridate)
redisConnect()
#getData from the DB

ppkeys = redisKeys('pp:*')
#data = redisMGet(ppkeys)
data = redisMGet(ppkeys[-grep("undefined", ppkeys)])

#put the unstructured data into a DF
cols = c( "UID",     "Session",        "lat",             "long",            "city",           
  "region",          "country",         "pictureName",     "pictureLocation",
  "pictureTopic",    "prevPictureID",   "prevPictureSec",  "pictureID"      ,
 "pictureSec",      "time")


dataDF = array(0, c(length(data), length(cols)))
for(i in 1:length(data)){
  dataDF[i, ] = unlist(fromJSON(data[[i]]))[cols] 
}
colnames(dataDF) = cols
dataDF = as.data.frame(dataDF)

dataDF$time = as.numeric(as.character(dataDF$time))

dataDF$timeDate = as.POSIXct(dataDF$time/1000, origin="1970-01-01")

```

### By Unique Users

```{r echo=FALSE}
byIDs = dataDF %.%
  arrange(time) %.%
  group_by(UID) %.%
  summarize(picturesClicked=length(UID),
            sessions=length(unique(Session)),
            topics=length(unique(pictureTopic)),
            medTimeBetweenClicks=quantile(ifelse(diff((time))>60*1000, NA, diff((time))/1000),.5,na.rm = T),
            totalTime=(max(time)-min(time))/1000
            ) %.%
  mutate(activeTime=medTimeBetweenClicks*picturesClicked)
            
  renderDataTable({byIDs})

byIDsSummary = byIDs %.%
  summarize(uniqueIDs=length(UID),
            medianSessionsperID=quantile(sessions, .5),
            medianClicked=quantile(picturesClicked, .5),
            sdClicked=sd(picturesClicked),
            medianTopics=quantile(topics, .5),
            medianTimeBetweenClicks=quantile(medTimeBetweenClicks, .5),
            sdTimeBetweenClicks=sd(medTimeBetweenClicks),
            medianTotalTime=quantile(totalTime, .5),
            sdTotalTime=sd(totalTime),
            medianActiveTime=quantile(activeTime, .5),
            sdActiveTime=sd(medianActiveTime)
            )
renderDataTable({byIDsSummary})
```

### By Unique Sessions

```{r echo=FALSE}

bySession = dataDF %.%
  arrange(time) %.%
  group_by(Session) %.%
  summarize(picturesClicked=length(UID),
            topics=length(unique(pictureTopic)),
            medTimeBetweenClicks=quantile(ifelse(diff((time))>60*1000, NA, diff((time))/1000),.5,na.rm = T),
            totalTime=(max(time)-min(time))/1000
            ) %.%
   summarize(medianClicked=quantile(picturesClicked, .5),
            sdClicked=sd(picturesClicked),
            medianTopics=quantile(topics, .5,na.rm = T),
            medianTimeBetweenClicks=quantile(medTimeBetweenClicks, .5,na.rm = T),
            sdTimeBetweenClicks=sd(medTimeBetweenClicks),
            medianTotalTime=quantile(totalTime, .5,na.rm = T),
            sdTotalTime=sd(totalTime)
            )
            
  renderDataTable({bySession})


```

### By GeoRegion

```{r echo=FALSE}

byRegion = dataDF %.%
  arrange(time) %.%
  group_by(city, region) %.%
  summarize(picturesClicked=length(UID),
            topics=length(unique(pictureTopic)),
            medTimeBetweenClicks=quantile(ifelse(diff((time))>60*1000, NA, diff((time))/1000),.5,na.rm = T),
            totalTime=(max(time)-min(time))/1000
            ) %.%
  arrange(desc(picturesClicked))
# %.%
#    summarize(medianClicked=quantile(picturesClicked, .5),
#             sdClicked=sd(picturesClicked),
#             medianTopics=quantile(topics, .5),
#             medianTimeBetweenClicks=quantile(medTimeBetweenClicks, .5),
#             sdTimeBetweenClicks=sd(medTimeBetweenClicks),
#             medianTotalTime=quantile(totalTime, .5),
#             sdTotalTime=sd(totalTime)
#             )
            
  renderDataTable({byRegion})


```
### By Picture Location

```{r echo=FALSE}

## need to change these metrics to be calculated per session or topic and given as a proportion
byPicLocation = dataDF %.%
  arrange(time) %.%
  group_by(pictureLocation) %.%
  summarize(picturesClicked=length(UID),
            topics=length(unique(pictureTopic)),
            medTimeBetweenClicks=quantile(ifelse(diff((time))>60*1000, NA, diff((time))/1000),.5,na.rm = T),
            totalTime=(max(time)-min(time))/1000
            ) %.%
  arrange(desc(picturesClicked))
# %.%
#    summarize(medianClicked=quantile(picturesClicked, .5),
#             sdClicked=sd(picturesClicked),
#             medianTopics=quantile(topics, .5),
#             medianTimeBetweenClicks=quantile(medTimeBetweenClicks, .5),
#             sdTimeBetweenClicks=sd(medTimeBetweenClicks),
#             medianTotalTime=quantile(totalTime, .5),
#             sdTotalTime=sd(totalTime)
#             )
            
  renderDataTable({byPicLocation})


```


### By Search Phrase
```{r echo=FALSE}
#also need to change this to the proportion of the user's time rather than a straight up calculation

byTopic = dataDF %.%
  arrange(time) %.%
  group_by(pictureTopic) %.%
  summarize(picturesClicked=length(UID),
            #topics=length(unique(pictureTopic)),
            medTimeBetweenClicks=quantile(ifelse(diff((time))>60*1000, NA, diff((time))/1000),.5,na.rm = T),
            totalTime=(max(time)-min(time))/1000
            ) %.%
  arrange(desc(picturesClicked))
# %.%
#    summarize(medianClicked=quantile(picturesClicked, .5),
#             sdClicked=sd(picturesClicked),
#             medianTopics=quantile(topics, .5),
#             medianTimeBetweenClicks=quantile(medTimeBetweenClicks, .5),
#             sdTimeBetweenClicks=sd(medTimeBetweenClicks),
#             medianTotalTime=quantile(totalTime, .5),
#             sdTotalTime=sd(totalTime)
#             )
            
  renderDataTable({byTopic})


```

### By Picture (and PrevPicture)


### This picture goes to these pictures (first column is the "prevPicture", 2,3,4,5 columns are the most probably next pictures)

### Views over Time

### Predictive Modeling